Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-11-19 Thesis/chapter/062-post-emma.tex
anova first draft

\label{sec:res-post-emma}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{ANOVA}\label{sec:res-anova}
\textbf{EMMA}
The \gls{rf} produced by the last iteration of \gls{emma} put a high \td{significance} 
on the calcination temperature $T_{cal}$. 
Now \gls{anova} can be used to check if the data 
From emma we saw that TCal seems to hav the biggest influence on 
both gamma and rho.

\textbf{What can/did we test?}
With anova we can check if the probability of arriving at these results was by pure chance or not. 
With the null hypothesis that we arrive at results by pure chance and of that the probability. 
We tested for each input variable the influence on rho and gamma 
and also as a test on vcal and $\lambda$. 
We used an alpha value of 0.05 which means that 1 out of 20 times this result could be 
produced by pure chance. 
If the f-value is below that value, then we choose to accept, that the data is not due to
chance but due to the influence of the independent variables on the dependent variables. 
Usually, the alpha-value is choosen to be 0.01-0.05\cite{hoffman2020concept,sellke2001pvalues}
The choice of a relatively high alpha-value is gerechetfertigt by the rather small amount of data and \td{evn}.
\td{could test anova on difference generation data sets}

\textbf{What were the results?}
\td{anova shows that for the mentioned indep and dep pairs, the means divieded by 
indep groups are not equal and that there is at least one group that is different. 
Important to mention, that anova uses categorical data for inputs, 
where our data is numerical and thus information is lost}
For both gamma and lambda (for both the emma dataset and the extended dataset) 
the F values for Tcal were in all cases under 0.01, 
indicating a real influence of Tcal on the conductance.
Both datasets exhibit a $p(>F) < 0.05$ for the interaction Tcal:vcal on phd. 
\td{why tcal:vcal on phd the same for both datasets?}
And the extended data set has pF samll er than 0.01 of vcal on phd.

\textbf{What do the results mean?} 
Anova bestaetigt that TCal has influence on both G and phd. 
\td{how to interpret p-values of 0.01 and 0.05? 
They mean that under the assumption that the null hypothesis is correct, 
there is a 1\% and 5\% chance of arriving at such data as observed.}
It seems that the probability of getting such data per chance that Tcal has no influence 
(null hypothesis is true) is less then 5\% (even less than 1\%). \td{NO bcs \cite{sellke2001pvalues}}

>>>>

\label{sec:res-post-emma}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsubsection{ANOVA}\label{sec:res-anova}
\textbf{EMMA}
The \gls{rf} produced by the last iteration of \gls{emma} put a high \td{significance} 
on the calcination temperature $T_{cal}$ with regard to the \td{measurables} of the conductance. 
\Gls{anova} is used to double check this. 
%Now \gls{anova} can be used to check if the data

\textbf{What can/did we test?}
With \gls{anova} we can check if the probability of arriving at these results was by pure chance or not. 
The null hypothesis is that the results were obtained by pure chance without any dependence of the insulation of a sample on the process variables.
%We tested for each input variable the influence on rho and gamma 
A one-way \gls{anova} was performed for every independent variable on $\rho$ and $\gamma$. 
%and also as a test on vcal and $\lambda$. 
We used an $\alpha$ value of 0.05 which means that 
the null hypothesis is rejected if the p-value is under 0.05. 
Usually, the $\alpha$-value is chosen to be 0.01 or 0.05\cite{hoffman2020concept,sellke2001pvalues}.
The choice of a relatively high alpha-value is motivated by the rather small amount of data and low \td{EPV}.
As mentioned by Sellke et al.\cite{sellke2001pvalues} a p-value of 0.05 might tempt 
to guess that in 1 out of 20 cases the results could be false positives, 
whereas the frequency is much higher. 
%1 out of 20 times this result could be 
%produced by pure chance given that the null hypothesis is true. 
%If the p-value is below that value, then we choose to accept, that the data is not due to
%chance but due to the influence of the independent variables on the dependent variables. 
\td{could test anova on difference generation data sets}

\textbf{What were the results?}
%\Gls{anova} shows that for the mentioned indep and dep pairs, the means divided by 
%indep groups are not equal and that there is at least one group that is different. 
For both $\rho$ and $\lambda$ (for both the \gls{emma} dataset and the extended dataset) 
the F values for $T_{cal}$ were in all cases under 0.01, 
indicating a real influence of $T_{cal}$ on the conductance.
Both datasets exhibit a p-value $< 0.05$ for the interaction $T_{cal}$:$v_{cal}$ on $\rho$.
\td{And the extended data set has p-value smaller than 0.01 of vcal on phd. 
Whereas vcal on phd for \gls{emma} dataset has p-value of slightly over 0.05.}
\td{why tcal:vcal on phd the same for both datasets? zufall}

\textbf{What do the results mean?} 
Anova bestaetigt that TCal has influence on both G and phd. 
\td{how to interpret p-values of 0.01 and 0.05? 
They mean that under the assumption that the null hypothesis is correct, 
there is a 1\% and 5\% chance of arriving at such data as observed.}
It seems that the probability of getting such data per chance that Tcal has no influence 
(null hypothesis is true) is less then 5\% (even less than 1\%). \td{NO bcs \cite{sellke2001pvalues}}
Important to mention, that anova uses categorical data for inputs, 
where our data is numerical and thus information is lost
